---
fontsize: 11pt
link-citations: TRUE
colorlinks: TRUE
editor_options:
  chunk_output_type: console
toc: TRUE
toc-title: \phantom{Contents}
toc-title-spacing: -1.5em
toc-spacing-after: 1em
toc-margin: 0.5in
linestretch: 1.15
biblio-style: econometrica.bst
bibliography: main.bib
output: oakdown::pdf_note
header-includes:
  - \usepackage{oaktex}
---

```{r title, results = "asis", echo = FALSE, mysize = NULL}
title <- "TITLE"
subtitle <- "SUBTITLE"
other <- "OTHER"
id <- "ID"
oakdown_print_title(title, subtitle, other, id)
```

```{r}
Sys.time()
```

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.
The quick brown fox jumped over the lazy dog.

## Theorem and Proof

Theorem \@ref(thm:label) is an example of an environment written with fenced divs.

:::{.thm data-latex="{Title of Theorem}{label}"}
This is an important theorem.
:::
:::{.pr data-latex=""}
Because I said so.
:::

## Lists

- This is an unordered list.
- Level 1 uses bullets. This is a long line. 
  This is a long line.
  This is a long line.
  This is a long line.
  This is a long line.
  This is a long line.
  This is a long line.
  - Level 2 uses dashes.
    - Level 3 uses open circles.
  - Next, we'll go over ordered lists.

1. This is an ordered list.
2. Do the numbers change depending on the levels?
    1. Level 2 is the same as Level 1.
        1. Level 3 is also the same.
        1. Level 3 is also the same.
    2. Pretty cool, right?
