---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# oakdown

<!-- badges: start -->
<!-- badges: end -->

The goal of {oakdown} is to store and create single-document and multi-document templates that are so compatible that it is easy to switch between these templates.

## Installation

You can install oakdown from [github](https://github.com/omkarakatta/oakdown) with:

``` r
install.packages("oakdown")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(oakdown)
## basic example code
```

## NOTES

- See [dotfiles](https://github.com/omkarakatta/dotfiles)
  - Store pandoc templates in `~/.pandoc/templates`.
    - Note that as of commit f86ca8e, I moved the `note.tex` pandoc template into `inst/rmarkdown/templates/note/resources/template.tex` to make the pandoc templates available via {oakdown}
  - Store/symlink bib files in `~/Library/texmf/bibtex/bib/misc`
  - Store/symlink bst files in `~/Library/texmf/bibtex/bst/misc`
  - Store input tex files in `~/Library/texmf/tex/latex/misc`
  - See:
    - [TeX Directory Structure](http://tug.org/tds/tds.html#Local-additions)
    - [SE post about storing .sty and .cls files](https://tex.stackexchange.com/questions/1137/where-do-i-place-my-own-sty-or-cls-files-to-make-them-available-to-all-my-te)
    - [Github Issue comment by @yasirs](https://github.com/rstudio/bookdown/issues/362#issuecomment-286327374)
- I would like the following formats (these are all PDF, but in the future, I'd like to learn how to create HTML and interactive versions):
  - note: single-document, go-to format
  - report: multi-document, looks very similar to a note
  - book: multi-document, operates like a report but looks and feels like a book
  - beamer: single-document presentation format
