```{r title, results = "asis", echo = FALSE, mysize = NULL}
title <- "my Note"
subtitle <- "my subtitle"
other <- "other"
devtools::load_all()
print_title(title, subtitle, other)
```

```{r}
sessionInfo()
```

```{r prelim}
library(knitr)
library(kableExtra)
```


# Hi

This is some text. The following is the Pythagorean theorem:
\begin{align*}
  a^{2}+b^{2}=c^{2}
  .
\end{align*}

This is some text. For $x \in \reals,$
\uss
\begin{align*}
  2x^{2} + 3 \cdot \Ind{x > 2}
\end{align*}

## Hello

:::: {.center data-latex=""}

::: {.minipage data-latex="{.5\linewidth}"}
This paragraph will be centered on the page, and
its width is 50% of the width of its parent element.
:::

::::

## This is a subsection

```{r}
kbl(head(mtcars), format = "latex", booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("striped"))
```

### subsubsection

This is a test.

[@R-knitr]

```{r}
getOption("tinytex.clean")
print("hello, world!")
if (TRUE) {
  rnorm(5)
}
```

\begin{align*}
  \Exp{X} &= \Exp{\CExp{X}{Y}} \\
  \Exp{X} &= \ExpB{\CExp{X}{Y}}
  .
\end{align*}

:::{.thm data-latex="{Title of Theorem}{test-theorem}"}
This is the Pythagorean Theorem:
\begin{align*}
  a^{2} + b^{2} = c^{2}.
\end{align*}
This is Theorem \@ref(thm:test-theorem)

- bullet A
- bullet B
- bullet C
:::
